From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/analysis.tex
[ACL2020] analysis: Table which subsumes Tasks1+2

>>>>

\begin{table*}[t]
	\centering
	\small
\begin{tabular}{ll||c|cccc|c}
	\toprule
	  &  & Hit & \multicolumn{4}{c|}{Human-like} & Off \\
	Model &  GT &  & SameObject &  OtherObject &  Low Count &  Related &   \\
	\midrule
	FRCNN--VG1600&VG &         74.8 &                13.7 &                  2.9 &              2.4 &              1.7 &          4.5 \\
	FRCNN--MN442&VG &         71.1 &                13.6 &                  3.4 &              2.0 &              2.6 &          7.4 \\
	\midrule
	FRCNN--VG1600--VGMN&MN &         80.7 &                 9.0 &                  2.0 &              1.8 &              3.4 &          3.3 \\
	\midrule
	ResNet101--VGMN&VG &         62.8 &                11.6 &                  2.1 &              3.2 &             10.3 &         10.1 \\
	ResNet101--MN442&VG &         63.8 &                11.9 &                  2.4 &              3.3 &              8.8 &          9.9 \\
	ResNet101--VGMN&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
	ResNet101--MN442&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\

	\bottomrule
\end{tabular}
\end{table*}
